---
title: "Market Scenario Example: Presentation"
output: 
  ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Scenario

## Background problem | Background & Problem

* Serious stock traders that take a technical approach can spend a lot of time monitoring indicators for dozens of portfolio assets

* A lack of an alert system may result in the trader being late in seeing an important buy or sell signal 

## Solution | Solution

* E*TRADE releases a new service that gives alerts once a certain market technical indicator reaches a given threshold. 
    * ex: Relative Strength Index (RSI) going above 70 suggests an asset is overbought
    
This saves the customer valuable time and improves use of technical indicators to increase gains, prevent losses, etc.

## Benefits | Benefits

* Gives E*TRADE customers a trading advantage over other platforms

* Helps technical traders with highly-diversified portfolios to keep track of buy/sell signals

## Execution | Execution

The proposed service works as such:

1. Customer enters technical indicator(s) and details or thresholds to be alerted for 
2. Email is sent with indicator details and a link to a customized webpage for that stock
3. Once on the page, a candle chart is displayed with charts and figures of the corresponding technical indicators

The user can set an option that pulls up charts of their other favorite indicators as well.

## Example | Example

1. Customer wants to be alerted when the RSI for any stock in their portfolio passes above 70
2. AAPL hits an RSI of over 70
3. Customer receives link to AAPL's stock page and summarized numbers
4. Webpage opens with candle chart and time series chart of RSI

# Design

## Budget | Budget

The proposed budget was listed as $50,000

```{r, echo=FALSE, warning=FALSE, message=FALSE}
### Make table
a <- c('Participant Incentives',
       'Financial and survey data collection',
       'Analysis, visualizations, and results write-up',
       'Safety net'
)
b <- c('$30,000', '$5,000', '$10,000', '$5,000')

prnt.df <- cbind(a, b)

### Print table
knitr::kable(prnt.df, col.names=NULL)
```
